### 2018-03-16 chapter2/ms.tex
Fixing Ch 2. Needs more proofreading

\section{Introduction}
\label{sec:ch2_intro}
The era of gravitational wave (GW) astronomy is fast approaching with the Advanced Laser Interferometer Gravitational Wave Observatory \citep[aLIGO,][]{LIGOMainRef} and advanced Virgo \citep[Virgo,][]{VirgoC7Burst} interferometers expected to make the first direct GW detections in the $2015-18$ time frame. These detectors will observe the GW signature resulting from the inspiral and merger of compact objects (e.g., neutron star-neutron star (NS-NS), solar mass black hole--black-hole (BH-BH), or NS-BH binaries). At design sensitivity, the ALIGO/AVIRGO network will be able to detect NS-NS mergers to an average distance of $\sim$ 200 Mpc \citep{Abadie+10} and with a typical localization region of $\sim$ 100 deg$^2$ \citep{Fairhurst2009,Nissanke+11,Aasi+14}. While this will be a remarkable achievement for both physics and astrophysics, the detection of an electromagnetic (EM) counterpart is essential to maximize the science obtained from a GW event. The identification of an EM counterpart will provide numerous benefits including: improved localization leading to host galaxy identification, determination of the distance and energy scales, identification of the progenitor local environment, and insight into the hydrodynamics of the merger \citep[see e.g.,][]{Sylvestre2003,Stubbs2008,Phinney2010,Stamatikos+09, Fong+10,MetzgerBerger12}. Furthermore, the detection of an EM counterpart will assist in breaking modeling degeneracies to obtain more accurate measurements of binary properties from the GW signal \citep{HughesHolz03}.

\clearpage
Extensive theoretical and observational work has been performed to understand the potential EM emission from a merging compact object binary. The range of potential counterparts covers the entire EM spectrum. The most popular counterpart is a short-hard gamma-ray burst \citep[SGRB; e.g.,][]{Paczynski1986,Narayan+92,Berger2014} powered by rapid accretion onto the compact remnant which leads to a strongly beamed relativistic jet. The evidence for a connection between SGRBs and compact object mergers includes the association with older stellar populations than for long GRBs \citep{Berger+05,Bloom+06,Berger2011,Fong+11,Fong+13}, large physical offsets between the burst locations and their host galaxies indicative of progenitor kicks \citep{Fong+10, FongBerger13}, weak association with the underlying stellar light of their hosts \citep{Fong+10, FongBerger13}, and a lack of association with supernovae \citep{Fox+05,Soderberg+06,Berger2010,FongBerger13,Berger2014}. The relativistic jet can also be observed in the x-ray, optical, and radio as non-thermal afterglow emission arises from interaction with the ambient medium. This emission is also affected by relativistic beaming but may still be seen off-axis as the jet decelerates and expands. In particular, for large off-axis angles $(\theta\gtrsim 2 \theta_j)$ the emission will be most pronounced in the radio on timescales of weeks to years \citep{NakarPiran11,MetzgerBerger12}.

@@

\clearpage
\singlespace
\begin{deluxetable}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Expected Rates For Fast Transients}
\tablehead{
\colhead{Object}&  \colhead{$\mathcal{R}_{\rm vol}$}& \colhead{$z_{\rm max}$}  &  \colhead{$\mathcal{R}_{\rm area}$} &  \colhead{$N$}     &     \colhead{Reference}      \\
\colhead{} & \colhead{(Mpc$^{-3}$ yr$^{-1}$)} & \colhead{} & \colhead{(deg$^{-2}$ yr$^{-1}$)} &  \colhead{} & \colhead{} }
\startdata
 Type .Ia    &                  10$^{-6}$                   &  0.5        &  $0.7$            &         1.4  & \citet{Bildsten+07} \\
 WD-NS mergers  &                  10$^{-5}$                   &   0.06        & $2\times10^{-2}$              &         $3\times10^{-2}$  &     \citet{Thompson+09}     \\
 WD-BH mergers  &      10$^{-5}$                   &    0.06        &   $2\times10^{-2}$              &      $3\times10^{-2}$  &    \citet{Fryer+99}          \\
AIC       &                  10$^{-6}$                   & 0.06        & $2\times10^{-3}$            &        $3\times10^{-3}$ &  \citet{Darbha+10}   \\
ELDD      &                  3$\times 10^{-7}$                   & 0.14        &    $6\times10^{-3}$           &      $1\times10^{-2}$ &  $\cdots$  \\
Pan-STARRS fast &                  5$\times 10^{-6}$                   &     0.5        &   $3.5$            &     7 &   \citet{Drout+14}
\enddata
\tablecomments{Expected rates for the various contaminants considered in \cref{sec:ch2_contaminants}. $\mathcal{R}_{\rm area}$ is computed assuming an isotropic distribution of sources in a volume defined by the comoving volume at $z_{\rm max}$.  The column $N$ refers to the number of events expected during a search covering 100 deg$^2$ for 7 days. See \cref{sec:ch2_rates} or details.}
\label{tab:ch2_rates}
\end{deluxetable}

@@

\clearpage
\begin{landscape}
\singlespace
\begin{deluxetable}{ccccc|cccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Required 5$\sigma$ Limiting Magnitudes for Kilonova Detection}
\tablehead{\colhead{Filter} & \multicolumn{4}{c|}{With Pre-Existing Template} & \multicolumn{4}{c}{Without Pre-Existing Template} \\
\colhead{} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \multicolumn{1}{c|}{Strategy \#4} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \colhead{Strategy \#4}}
\startdata
$r$ & 24.9 (25.9) & 25.0 (25.9) & 24.5 (25.5) & 24.5 (25.5) & 25.0 (25.9) & 25.0 (25.9) & 25.0 (25.9) & 25.1 (25.9) \\
$i$ & 23.2 (23.9) & 23.3 (24.0) & 22.9 (23.9) & 22.9 (23.9) & 24.0 (24.9) & 24.3 (25.0) & 24.0 (24.9) & 24.3 (25.0) \\
$z$ & 22.2 (22.9) & 22.4 (23.2) & 22.1 (22.9) & 22.1 (23.0) & 23.1 (23.9) & 23.2 (24.0) & 23.1 (23.9) & 23.5 (24.2)
\enddata
\tablecomments{\,Limiting magnitudes $(5\sigma)$ required to detect 50\% (95\%) of kilonovae as a function of observing strategy and filter (\cref{sec:ch2_MCsims_det}, \Cref{fig:ch2_det}). Values are averaged over all start times. We compute the required depths for follow-up observations with and without a pre-existing template (\cref{sec:ch2_diff}).}
\label{tab:ch2_det}
\end{deluxetable}
\end{landscape}

@@

\subsection{Neutrino Driven Winds}
\label{sec:ch2_neutrino}
Ejecta can be produced by the outflows from a post-merger accretion disk \citep{Dessart+09,FernandezMetzger13,Fernandez+15}. \citet{FernandezMetzger13} performed numerical two-dimensional hydrodynamical simulations of accretion disks and found that $\sim$10\% of the initial disk mass is ejected over timescales of $\sim1$ s. These ejecta are a neutron-rich wind with an electron fraction of $Y_{\text{e}} \sim 0.2$, producing conditions that are favorable for r-process nucleosynthesis. This type of outflow will therefore not drastically alter the observational properties of the kilonova.

\clearpage
Recent work by \citet{Fernandez+15} found that the amount of ejected mass is a function of the spin of the remnant black hole, with more rapidly spinning black holes leading to higher ejecta masses by a factor of several. Furthermore, they found that $Y_{{\rm e}}$ increased monotonically with black hole spin due to an increased early-time neutrino luminosity from a rapidly spinning black hole. They found that in the most extreme cases $(a \gtrsim 0.8)$, the system could eject $\sim10^{-5} - 3\times10^{-3}\;M_{\odot}$ of material with $Y_{{\rm e}} \gtrsim 0.25$. Specifically, an ejecta mass of $\sim10^{-3}\;M_{\odot}$ will produce a blue component in the kilonovae light curve with $\nu L_{\nu} \approx 7.5\times10^{40}$ erg s$^{-1}$ at $\sim6500$ \AA \; ($r \approx 22.5$ mag at 200 Mpc) and a peak time of $\lesssim$ 1 day \citep{Kasen+15}. This is significantly brighter in $r$-band than the kilonovae models discussed previously, but the short timescales make observing this component challenging.

@@

\section{Follow-Up Strategies}
\label{sec:ch2_disc}
Motivated by the results of our simulated observations, we now assess the most effective methodologies for conducting efficient GW follow-up observations. There are two primary issues to address: The detection of a kilonovae, and its identification against a population of contaminant sources. Our simulations show that, in the case of a pre-existing template, observations which achieve a depth of $i\approx24$ mag and $z\approx23$ mag lead to the detection of about 95\% of kilonovae. Furthermore, observations should commence within 12 hours of the GW trigger to maximize the likelihood of detecting the source during the rise to peak. We also show that cuts made on $i-z$ color, the rise time (if available), and $\Delta m_z$ are strong discriminants for separating a kilonova from the contaminant population. Quantitatively, with $i-z\gtrsim0$ mag, a rise time of $\lesssim 4$ days, and $|\Delta m_z| \gtrsim 0.4$ mag, we can eliminate a significant fraction $(\gtrsim95\%)$ of contaminants without removing any kilonovae. If the source is seen in decline then requiring $i-z\gtrsim0$ mag and $|\Delta m_z| \gtrsim 0.4$ mag are still strong cuts, eliminating $\sim60\%$ of contaminants. If we also require a decline time of $\lesssim 5$ days then we can eliminate $\gtrsim 90\%$ of contaminants, however this cut eliminates nearly half of the kilonova population. These results do not depend strongly on the choice of cadence (i.e., there is no benefit from intra-night observations). Therefore, follow-up observations should include a single visit per filter per night for at least the first few nights following a trigger.

@@

\clearpage
\begin{landscape}
\singlespace
\begin{deluxetable}{cccccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Follow-up Capabilities of Wide-Field Telescopes}
\tablehead{\multicolumn{3}{c}{} & \multicolumn{2}{c}{{\em r}-band} & \multicolumn{2}{c}{{\em i}-band} & \multicolumn{2}{c}{{\em z}-band} & \multicolumn{1}{c}{} \\
\colhead{Instrument} & \colhead{FoV} & \colhead{Etendue} & \colhead{Exp.} & \colhead{Rate}  & \colhead{Exp.}  &\colhead{Rate} & \colhead{Exp.} & \colhead{Rate} &  \colhead{$i + z$ Rate} \\
\colhead{} & \colhead{(deg$^2$)} & \colhead{(m$^2$ deg$^2$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} &  \colhead{(deg$^2$ hr$^{-1}$)}}
\startdata
DECam$^{{\rm a}}$ & 3 &  37.7 & 4200 & 2.5 & 250 & 43 & 150 & 72 & 27  \\
ZTF$^{{\rm b}}$ & 47 & 53.2 & $9\times10^5$  & 0.2 & 1.6$\times10^4$ & 10 & {\bf --} & {\bf --}  & {\bf --}   \\
Subaru HSC$^{{\rm c}}$  & 1.8  & 90.5 & 520 & 12 & 55 & 115 & 45 & 145 & 65 \\
Pan-STARRS2$^{{\rm d}}$ & 14 & 35.6 & $1.4\times10^4$  & 4 & 700  & 72 & 350 & 144  & 30 \\
LSST$^{{\rm e}}$ & 9.6 & 315 & 390 & 88 & 28 & 1235  & 19 & 1820 & 735
\enddata
\tablecomments{Expected rates of sky coverage in deg$^2$ hr$^{-1}$ for several existing and future wide-field facilities at a depth of $r\approx26$ mag, $i\approx24$ mag and $z\approx23$ mag (i.e., the depths necessary to achieve a 95\% detection rate for kilonovae). We note that for HSC and LSST we include overhead times of 20s and 2s, respectively, as they are comparable to the exposure times.
References: \begin{enumerate}[label=\alph*,topsep=5pt]
\item DECam ETC, \url{http://www.ctio.noao.edu/noao/content/Exposure-Time-Calculator-ETC-0}
\item \citet{Nissanke+13,KasliwalNissanke14}
\item HSC ETC, \url{http://www.naoj.org/cgi-bin/img_etc.cgi}
\item Pan-STARRS DRM, \url{http://pan-starrs.ifa.hawaii.edu/}
\item LSST ETC, \url{http://dls.physics.ucdavis.edu:8080/etc4_3work/servlets/LsstEtc.html}
\end{enumerate}
}
\label{tab:ch2_tele}
\end{deluxetable}
\end{landscape}

>>>>

\section{Introduction}
\label{sec:ch2_intro}
The era of gravitational wave (GW) astronomy is fast approaching with the Advanced Laser Interferometer Gravitational Wave Observatory \citep[aLIGO,][]{LIGOMainRef} and advanced Virgo \citep[Virgo,][]{VirgoC7Burst} interferometers expected to make the first direct GW detections in the $2015-18$ time frame. These detectors will observe the GW signature resulting from the inspiral and merger of compact objects (e.g., neutron star-neutron star (NS-NS), solar mass black hole--black-hole (BH-BH), or NS-BH binaries). At design sensitivity, the ALIGO/AVIRGO network will be able to detect NS-NS mergers to an average distance of $\sim$ 200 Mpc \citep{Abadie+10} and with a typical localization region of $\sim$ 100 deg$^2$ \citep{fairhurst2009,Nissanke+11,Aasi+14}. While this will be a remarkable achievement for both physics and astrophysics, the detection of an electromagnetic (EM) counterpart is essential to maximize the science obtained from a GW event. The identification of an EM counterpart will provide numerous benefits including: improved localization leading to host galaxy identification, determination of the distance and energy scales, identification of the progenitor local environment, and insight into the hydrodynamics of the merger \citep[see e.g.,][]{Sylvestre2003,Stubbs2008,Phinney2010,Stamatikos+09, Fong+10,MetzgerBerger12}. Furthermore, the detection of an EM counterpart will assist in breaking modeling degeneracies to obtain more accurate measurements of binary properties from the GW signal \citep{HughesHolz03}.

\clearpage
Extensive theoretical and observational work has been performed to understand the potential EM emission from a merging compact object binary. The range of potential counterparts covers the entire EM spectrum. The most popular counterpart is a short-hard gamma-ray burst \citep[SGRB; e.g.,][]{Paczynski1986,Narayan+92,Berger2014} powered by rapid accretion onto the compact remnant which leads to a strongly beamed relativistic jet. The evidence for a connection between SGRBs and compact object mergers includes the association with older stellar populations than for long GRBs \citep{Berger+05,Bloom+06,Berger2011,Fong+11,Fong+13}, large physical offsets between the burst locations and their host galaxies indicative of progenitor kicks \citep{fong+10, FongBerger13}, weak association with the underlying stellar light of their hosts \citep{fong+10, FongBerger13}, and a lack of association with supernovae \citep{fox+05,Soderberg+06,Berger2010,FongBerger13,Berger2014}. The relativistic jet can also be observed in the x-ray, optical, and radio as non-thermal afterglow emission arises from interaction with the ambient medium. This emission is also affected by relativistic beaming but may still be seen off-axis as the jet decelerates and expands. In particular, for large off-axis angles $(\theta\gtrsim 2 \theta_j)$ the emission will be most pronounced in the radio on timescales of weeks to years \citep{NakarPiran11,MetzgerBerger12}.

@@

\clearpage
\singlespace
\begin{deluxetable}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Expected Rates For Fast Transients}
\tablehead{
\colhead{Object}&  \colhead{$\mathcal{R}_{\rm vol}$}& \colhead{$z_{\rm max}$}  &  \colhead{$\mathcal{R}_{\rm area}$} &  \colhead{$N$}     &     \colhead{Reference}      \\
\colhead{} & \colhead{(Mpc$^{-3}$ yr$^{-1}$)} & \colhead{} & \colhead{(deg$^{-2}$ yr$^{-1}$)} &  \colhead{} & \colhead{} }
\startdata
 Type .Ia    &                  10$^{-6}$                   &  0.5        &  $0.7$            &         1.4  & \citet{Bildsten+07} \\
 WD-NS mergers  &                  10$^{-5}$                   &   0.06        & $2\times10^{-2}$              &         $3\times10^{-2}$  &     \citet{Thompson+09}     \\
 WD-BH mergers  &      10$^{-5}$                   &    0.06        &   $2\times10^{-2}$              &      $3\times10^{-2}$  &    \citet{fryer+99}          \\
AIC       &                  10$^{-6}$                   & 0.06        & $2\times10^{-3}$            &        $3\times10^{-3}$ &  \citet{Darbha+10}   \\
ELDD      &                  3$\times 10^{-7}$                   & 0.14        &    $6\times10^{-3}$           &      $1\times10^{-2}$ &  $\cdots$  \\
Pan-STARRS fast &                  5$\times 10^{-6}$                   &     0.5        &   $3.5$            &     7 &   \citet{Drout+14}
\enddata
\tablecomments{Expected rates for the various contaminants considered in \cref{sec:ch2_contaminants}. $\mathcal{R}_{\rm area}$ is computed assuming an isotropic distribution of sources in a volume defined by the comoving volume at $z_{\rm max}$.  The column $N$ refers to the number of events expected during a search covering 100 deg$^2$ for 7 days. See \cref{sec:ch2_rates} or details.}
\label{tab:ch2_rates}
\end{deluxetable}

@@

\clearpage
\begin{landscape}
\singlespace
\begin{deluxetable}{ccccc|cccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Required 5$\sigma$ Limiting Magnitudes for Kilonova Detection}
\tablehead{\colhead{filter} & \multicolumn{4}{c|}{With Pre-Existing Template} & \multicolumn{4}{c}{Without Pre-Existing Template} \\
\colhead{} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \multicolumn{1}{c|}{Strategy \#4} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \colhead{Strategy \#4}}
\startdata
$r$ & 24.9 (25.9) & 25.0 (25.9) & 24.5 (25.5) & 24.5 (25.5) & 25.0 (25.9) & 25.0 (25.9) & 25.0 (25.9) & 25.1 (25.9) \\
$i$ & 23.2 (23.9) & 23.3 (24.0) & 22.9 (23.9) & 22.9 (23.9) & 24.0 (24.9) & 24.3 (25.0) & 24.0 (24.9) & 24.3 (25.0) \\
$z$ & 22.2 (22.9) & 22.4 (23.2) & 22.1 (22.9) & 22.1 (23.0) & 23.1 (23.9) & 23.2 (24.0) & 23.1 (23.9) & 23.5 (24.2)
\enddata
\tablecomments{\,Limiting magnitudes $(5\sigma)$ required to detect 50\% (95\%) of kilonovae as a function of observing strategy and filter (\cref{sec:ch2_MCsims_det}, \Cref{fig:ch2_det}). Values are averaged over all start times. We compute the required depths for follow-up observations with and without a pre-existing template (\cref{sec:ch2_diff}).}
\label{tab:ch2_det}
\end{deluxetable}
\end{landscape}

@@

\subsection{Neutrino Driven Winds}
\label{sec:ch2_neutrino}
Ejecta can be produced by the outflows from a post-merger accretion disk \citep{Dessart+09,FernandezMetzger13,Fernandez+15}. \citet{fernandezMetzger13} performed numerical two-dimensional hydrodynamical simulations of accretion disks and found that $\sim$10\% of the initial disk mass is ejected over timescales of $\sim1$ s. These ejecta are a neutron-rich wind with an electron fraction of $Y_{\text{e}} \sim 0.2$, producing conditions that are favorable for r-process nucleosynthesis. This type of outflow will therefore not drastically alter the observational properties of the kilonova.

\clearpage
Recent work by \citet{fernandez+15} found that the amount of ejected mass is a function of the spin of the remnant black hole, with more rapidly spinning black holes leading to higher ejecta masses by a factor of several. Furthermore, they found that $Y_{{\rm e}}$ increased monotonically with black hole spin due to an increased early-time neutrino luminosity from a rapidly spinning black hole. They found that in the most extreme cases $(a \gtrsim 0.8)$, the system could eject $\sim10^{-5} - 3\times10^{-3}\;M_{\odot}$ of material with $Y_{{\rm e}} \gtrsim 0.25$. Specifically, an ejecta mass of $\sim10^{-3}\;M_{\odot}$ will produce a blue component in the kilonovae light curve with $\nu L_{\nu} \approx 7.5\times10^{40}$ erg s$^{-1}$ at $\sim6500$ \AA \; ($r \approx 22.5$ mag at 200 Mpc) and a peak time of $\lesssim$ 1 day \citep{Kasen+15}. This is significantly brighter in $r$-band than the kilonovae models discussed previously, but the short timescales make observing this component challenging.

@@

\section{follow-Up Strategies}
\label{sec:ch2_disc}
Motivated by the results of our simulated observations, we now assess the most effective methodologies for conducting efficient GW follow-up observations. There are two primary issues to address: The detection of a kilonovae, and its identification against a population of contaminant sources. Our simulations show that, in the case of a pre-existing template, observations which achieve a depth of $i\approx24$ mag and $z\approx23$ mag lead to the detection of about 95\% of kilonovae. Furthermore, observations should commence within 12 hours of the GW trigger to maximize the likelihood of detecting the source during the rise to peak. We also show that cuts made on $i-z$ color, the rise time (if available), and $\Delta m_z$ are strong discriminants for separating a kilonova from the contaminant population. Quantitatively, with $i-z\gtrsim0$ mag, a rise time of $\lesssim 4$ days, and $|\Delta m_z| \gtrsim 0.4$ mag, we can eliminate a significant fraction $(\gtrsim95\%)$ of contaminants without removing any kilonovae. If the source is seen in decline then requiring $i-z\gtrsim0$ mag and $|\Delta m_z| \gtrsim 0.4$ mag are still strong cuts, eliminating $\sim60\%$ of contaminants. If we also require a decline time of $\lesssim 5$ days then we can eliminate $\gtrsim 90\%$ of contaminants, however this cut eliminates nearly half of the kilonova population. These results do not depend strongly on the choice of cadence (i.e., there is no benefit from intra-night observations). Therefore, follow-up observations should include a single visit per filter per night for at least the first few nights following a trigger.

@@

\clearpage
\begin{landscape}
\singlespace
\begin{deluxetable}{cccccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{follow-up Capabilities of Wide-Field Telescopes}
\tablehead{\multicolumn{3}{c}{} & \multicolumn{2}{c}{{\em r}-band} & \multicolumn{2}{c}{{\em i}-band} & \multicolumn{2}{c}{{\em z}-band} & \multicolumn{1}{c}{} \\
\colhead{Instrument} & \colhead{foV} & \colhead{Etendue} & \colhead{Exp.} & \colhead{Rate}  & \colhead{Exp.}  &\colhead{Rate} & \colhead{Exp.} & \colhead{Rate} &  \colhead{$i + z$ Rate} \\
\colhead{} & \colhead{(deg$^2$)} & \colhead{(m$^2$ deg$^2$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} &  \colhead{(deg$^2$ hr$^{-1}$)}}
\startdata
DECam$^{{\rm a}}$ & 3 &  37.7 & 4200 & 2.5 & 250 & 43 & 150 & 72 & 27  \\
ZTF$^{{\rm b}}$ & 47 & 53.2 & $9\times10^5$  & 0.2 & 1.6$\times10^4$ & 10 & {\bf --} & {\bf --}  & {\bf --}   \\
Subaru HSC$^{{\rm c}}$  & 1.8  & 90.5 & 520 & 12 & 55 & 115 & 45 & 145 & 65 \\
Pan-STARRS2$^{{\rm d}}$ & 14 & 35.6 & $1.4\times10^4$  & 4 & 700  & 72 & 350 & 144  & 30 \\
LSST$^{{\rm e}}$ & 9.6 & 315 & 390 & 88 & 28 & 1235  & 19 & 1820 & 735
\enddata
\tablecomments{Expected rates of sky coverage in deg$^2$ hr$^{-1}$ for several existing and future wide-field facilities at a depth of $r\approx26$ mag, $i\approx24$ mag and $z\approx23$ mag (i.e., the depths necessary to achieve a 95\% detection rate for kilonovae). We note that for HSC and LSST we include overhead times of 20s and 2s, respectively, as they are comparable to the exposure times.
References: \begin{enumerate}[label=\alph*,topsep=5pt]
\item DECam ETC, \url{http://www.ctio.noao.edu/noao/content/Exposure-Time-Calculator-ETC-0}
\item \citet{Nissanke+13,KasliwalNissanke14}
\item HSC ETC, \url{http://www.naoj.org/cgi-bin/img_etc.cgi}
\item Pan-STARRS DRM, \url{http://pan-starrs.ifa.hawaii.edu/}
\item LSST ETC, \url{http://dls.physics.ucdavis.edu:8080/etc4_3work/servlets/LsstEtc.html}
\end{enumerate}
}
\label{tab:ch2_tele}
\end{deluxetable}
\end{landscape}
